Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-03 ms.tex
rewrite of DECaLS catalog section

In $\S$\ref{sec:data} we briefly describe the W1/W2 single-exposure data set 
from which our coadds are constructed. In $\S$\ref{sec:coadd}, we review the 
important aspects of the unWISE coaddition framework we employ and list the 
processing features which are newly introduced in this work. In 
$\S$\ref{sec:calib} we describe an empirical photometric calibration we
derived in order to combine pre and post reactivation WISE images. In 
$\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
particularly scattered moonlight. In $\S$\ref{sec:recover} we describe
our procedure for recovering Moon-contaminated exposures. In 
$\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
of full-depth coadds generated by our processing. In $\S$\ref{sec:depth}, we 
present a preliminary investigation of the improvements in WISE depth which 
have resulted from doubling the amount of W1/W2 imaging. We conclude in 
$\S$\ref{sec:future} with a brief discussion of the work which still remains to
be done with existing and future NEOWISER imaging.

@@

\begin{figure*}[ht]
 \begin{center}
  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
  \caption{\label{fig:warp_example} Illustration of the procedure by which
           we recover Moon-contaminated exposures, as described in 
           $\S$\ref{sec:recover}. Shown here is quadrant 2
           of W1 exposure 05245b140. This quadrant was successfully recovered.
           The polynomial background correction is subtracted
           from every pixel in the L1b quadrant, but is shown masked
           for the sake of visual comparison to the masked L1b quadrant.}
% mention which tile used as reference?
 \end{center}
\end{figure*}

@@

\section{Preliminary Depth Characterization}
\label{sec:depth}

It is important to quantify the effect of increased coverage on
the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
relative to those based on the AllWISE-only coadds of \cite{lang14}. A
full characterization should systematically explore a range of 
ecliptic and galactic latitudes, to consider the full spectrum of interplay
between decreased statistical noise and confusion. For isolated sources in the 
sky noise limit, we would expect a doubling of the W1/W2 imaging data
to increase the depth in each band by 0.38 mag.

The only existing catalogs based on our AllWISE+NEOWISER coadds
are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
\citep[DECaLS,][]{decals}, which include W1-W4 forced photometry for all
optically detected sources. On the other hand, optical sources in DECaLS DR1
are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
Therefore, comparing the S/N of W1/W2 fluxes in DR2 versus DR1 can allow us to 
obtain estimates of the depth increases for regions of low ecliptic and high 
galactic latitude.

We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
higher S/N in W1 (W2). For comparison, the expectation based purely on
reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
S/N.

Much more work is needed to characterize the increased sensitivity
of WISE to faint sources due to the inclusion of NEOWISER
imaging, as this will inform forecasts about the final 3.4$\mu$m and 
4.6$\mu$m depths expected upon WISE's permanent retirement.

>>>>

In $\S$\ref{sec:data} we briefly describe the W1/W2 single-exposure data set 
from which our coadds are constructed. In $\S$\ref{sec:coadd}, we review the 
important aspects of the unWISE coaddition framework we employ and list the 
processing features which are newly introduced in this work. In 
$\S$\ref{sec:calib} we describe an empirical photometric calibration we
derived in order to combine pre and post reactivation WISE images. In 
$\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
particularly scattered moonlight. In $\S$\ref{sec:recover} we describe
our procedure for recovering Moon-contaminated exposures. In 
$\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
of full-depth coadds generated by our processing. In $\S$\ref{sec:depth} we 
present a catalog-level validation of the improvements in WISE depth
that result from doubling the amount of W1/W2 imaging. We conclude in 
$\S$\ref{sec:future} with a brief discussion of the work which still remains to
be done with existing and future NEOWISER imaging.

@@

\begin{figure*}[ht]
 \begin{center}
  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
  \caption{\label{fig:warp_example} Illustration of the procedure by which
           we recover Moon-contaminated exposures, as described in 
           $\S$\ref{sec:recover}. Shown here is quadrant 2
           of W1 exposure 05245b140. This quadrant was successfully recovered.
           The polynomial background correction is subtracted
           from every pixel in the L1b quadrant, but is shown masked
           for the sake of comparison to the masked L1b quadrant.}
% mention which tile used as reference?
 \end{center}
\end{figure*}

@@

\section{Catalog-level Validation}
\label{sec:depth}

It is important to quantify the effect of increased coverage on
the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
relative to those based on the AllWISE-only coadds of \cite{lang14}. A
complete characterization should systematically explore a range of 
ecliptic and galactic latitudes, to consider the full spectrum of interplay
between decreased statistical noise and confusion. For isolated sources in the 
sky noise limit, we would expect a doubling of the W1/W2 imaging data
to increase the depth in each band by 0.38 mag.

The only existing catalogs based on our AllWISE+NEOWISER coadds
are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
\citep[DECaLS,][]{decals}, which include W1-W4 forced photometry for all
optically detected sources. On the other hand, optical sources in DECaLS DR1
are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
Therefore, comparing the uncertainties on W1/W2 fluxes in DR2 versus DR1 can 
allow us to obtain estimates of the forced-photometry depth increases for 
regions of low ecliptic and high galactic latitude.

%We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
%faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
%in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
%higher S/N in W1 (W2). For comparison, the expectation based purely on
%reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
%S/N.

To make such a comparison, for each of W1 and W2, we select a sample of DECaLS 
DR2 sources with \verb|type|='PSF', \verb|wise_fracflux|$<$0.1, more than
one DECam observation, and WISE S/N within the range 10$\pm$1. We
then obtain a DR1-DR2 comparison sample by cross-matching these DR2 objects
with DR1 \verb|type|='PSF' sources, using a 1$''$ matching radius. The resulting
comparison samples have $\sim$415,000 objects. For such
sources, we find median reductions in WISE forced photometry uncertainties
of 1.38$\times$ (1.30$\times$) in W1 (W2). The corresponding median increase in
coverage is 1.9$\times$ in both bands, leading us to expect a factor of 
1.38$\times$ decrease in uncertainties based purely on reduced statistical 
noise.

These values are not intended to represent the enhanced
depths that would result from comparing WISE-only catalogs which begin with
a source detection step on the WISE coadds. Since the DR2 forced photometry 
does not attempt to account for faint, infrared-only sources which are
newly revealed in the AllWISE+NEOWISER stacks, the photometric uncertainty
reduction factors we have derived serve mostly as quantitative confirmation 
of the decreased statistical noise shown in Figure \ref{fig:image_noise}.

Much more work is needed to characterize the increased sensitivity
of WISE to faint infrared-only sources due to the inclusion of NEOWISER
imaging, as this will inform forecasts about the final 3.4$\mu$m and 
4.6$\mu$m depths expected upon WISE's permanent retirement.
